InnoDB's Full Text Search Dynamic article with Shiny/R

### 2016-02-02 article.rmd
CHanged to work locally as db4free died.

# You do not want clear passwords, but is a sandbox.
#con <- dbConnect(MySQL(),
#                 user="msandbox", password="msandbox", port=14901
#                 ,dbname="test", socket="/tmp/mysql_sandbox14901.sock",
#                 host="127.0.0.1")

con <- dbConnect(MySQL(),
                 user="ftsinnodb", password="elfilete", port=3306
                 ,dbname="ftsinnodb", #socket="/tmp/mysql_sandbox14901.sock",
                 host="db4free.net")

@@

@@

[Fine tuning](https://dev.mysql.com/doc/refman/5.7/en/fulltext-fine-tuning.html)

>>>>

# You do not want clear passwords, but is a sandbox.
con <- dbConnect(MySQL(),
                 user="msandbox", password="msandbox", port=13454
                 ,dbname="test", socket="/tmp/mysql_sandbox13454.sock",
                 host="127.0.0.1")

#con <- dbConnect(MySQL(),
#                 user="ftsinnodb", password="elfilete", port=3306
#                 ,dbname="ftsinnodb", #socket="/tmp/mysql_sandbox14901.sock",
#                 host="db4free.net")

@@

### Bug

```
emanuel@3laptop ~/sandboxes/rsandbox_5_7_9 $ ./m dumpTest < full.dump 
ERROR 182 (HY000) at line 73: Invalid InnoDB FTS Doc ID
```

It works if loaded ddl and data separately.

```
emanuel@3laptop ~/sandboxes/rsandbox_5_7_9 $ ./m dumpTest < ddl.dump 
emanuel@3laptop ~/sandboxes/rsandbox_5_7_9 $ ./m dumpTest < onlyData.dump 
emanuel@3laptop ~/sandboxes/rsandbox_5_7_9 $ ./m dumpTest < full.dump 
ERROR 182 (HY000) at line 73: Invalid InnoDB FTS Doc ID
```

Changed innodb_autoinc_lock_mode to 0 (old behavior) and 2, with the same results.
Looks like FTS in InnoDB does not like metadata locks (as we are using a single transaction
to load the data).

@@

[Fine tuning](https://dev.mysql.com/doc/refman/5.7/en/fulltext-fine-tuning.html)
[Performance](https://blogs.oracle.com/mysqlinnodb/entry/innodb_full_text_search_performance)
